taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-01-04 notebook/fuzzy-matching.Rmd
WIP on fuzzy matching

```{r}
url <- "ftp://ftpext.usgs.gov/pub/er/md/laurel/BBS/DataFiles/SpeciesList.txt"
col_names <- c("Seq", "AOU", "English_Common_Name", "French_Common_Name",
               "Spanish_Common_Name", "order", "family", "genus", "species")
bbs <- readr::read_table(url, 
                         skip = 9, 
                         col_names = col_names, 
                         col_types = "ccccccccc")
bbs <- bbs %>% mutate(species = paste(genus, species))
#readr::write_tsv(bbs, "inst/extdata/bbs.tsv")

>>>>

```{r}
read_tsv(system.file("extdata/bbs.tsv"))

### 2019-01-04 paper/manuscript.Rmd
WIP on fuzzy matching

```{r}
td_create("gbif")
```

```{r}
url <- "ftp://ftpext.usgs.gov/pub/er/md/laurel/BBS/DataFiles/SpeciesList.txt"
col_names <- c("Seq", "AOU", "English_Common_Name", "French_Common_Name",
               "Spanish_Common_Name", "ORDER", "Family", "Genus", "Species")
bbs <- readr::read_table(url, 
                         skip = 9, 
                         col_names = col_names, 
                         col_types = "ccccccccc")

@@

```{r}
species_list = paste(bbs$Genus, bbs$Species)
length(species_list)
```

```{r}
bbs_ids <- 
data_frame(species = species_list) %>% 
  mutate(gbif = get_ids(species, "gbif", "prefix"),
         col = get_ids(species, "col", "prefix"),
         itis = get_ids(species, "itis", "prefix"),
         ncbi = get_ids(species, "ncbi", "prefix"),
         wikidata = get_ids(species, "wd", "prefix"))

@@

>>>>

```{r}
td_create("all")
```

```{r}
url <- "ftp://ftpext.usgs.gov/pub/er/md/laurel/BBS/DataFiles/SpeciesList.txt"
col_names <- c("Seq", "AOU", "English_Common_Name", "French_Common_Name",
               "Spanish_Common_Name", "order", "family", "genus", "species")
bbs <- readr::read_table(url, 
                         skip = 9, 
                         col_names = col_names, 
                         col_types = "ccccccccc")
bbs <- bbs %>% mutate(species = paste(genus, species))
readr::write_tsv(bbs, "inst/extdata/bbs.tsv")

@@

```{r}
species_list = paste(bbs$genus, bbs$species)
length(species_list)
```

```{r}
bbs_ids <- 
data_frame(species = species_list) %>% 
  mutate(gbif = get_ids(species, "gbif", "prefix"),
          col = get_ids(species, "col", "prefix"),
         itis = get_ids(species, "itis", "prefix"),
         ncbi = get_ids(species, "ncbi", "prefix"),
     wikidata = get_ids(species, "wd", "prefix"),
         #iucn = get_ids(species, "iucn", "prefix"),
          ott = get_ids(species, "ott","prefix") 
  )

@@

```{r}
```
